

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Buena Fé

This is a GitHub repository holding public collaboration documentation and code for a collaborative project in Ecduador regarding transparency, institutional capacity, and citizen involvement between the [Inter-American Development Bank Andean Group](https://www.iadb.org/en/who-we-are/how-we-are-organized/departments-offices-and-sectors/country-department-andean-group) (liaised by Osmel Enrique Manzano and Daniela Sofia Valdivia Llerena), [FARO](https://grupofaro.org/areas-de-trabajo/extrayendo-transparencia/), a number of municipal governments, and Yale University (with [J Stallman, PhD Candidate in Economics liaising](https://stallman-j.github.io/)). 

If you're a collaborator on this project working with internal documentation and need access to files *not* housed in this repo, you should first get an account with [PCloud](https://www.pcloud.com/), a virtual drive that's like Dropbox but with nicer storage properties. Also download the Pcloud drive so that you can edit and view folders locally on your computer. 

Once you've done this, email [J](mailto:j.stallman@yale.edu) who will send you the share link for our folders.

## Why Buena Fé?

The title of this repository borrows from the "ideal thought experiment". To determine the effect of a particular intervention, one would ideally implement this intervention in randomly selected units. For this particular project, we'll be implementing a transparency initiative at the level of the canton (municipio) in Ecuador.

It's rarely feasible to randomly select a geography in which to implement an intervention. However, nothing's stopping us from selecting our project name in this manner! 

Buena Fé was therefore chosen among Ecuador's 221 cantons at random. We think it's an auspicious sign.

You can see a vignette of the R code which implemented this randomization [here](https://stallman-j.github.io/ekonomR/vignettes/basic-mapping/).

```{r, echo = FALSE, fig.cap = "Buena Fé in Ecuador"}
url <- paste0("https://github.com/stallman-j/buena-fe/blob/main/output/03_maps/",paste0("Ecuador_with_1_at-gadm-level_2_randomly-chosen.png?raw=true"))

knitr::include_graphics(url)

```
