

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Buena Fé

This is a GitHub repository holding public collaboration documentation and code for a collaborative project regarding transparency in Ecuador, institutional capacity, and citizen involvement between the [Inter-American Development Bank Andean Group](https://www.iadb.org/en/who-we-are/how-we-are-organized/departments-offices-and-sectors/country-department-andean-group) (liaised by Osmel Enrique Manzano and Daniela Sofia Valdivia Llerena), [FARO](https://grupofaro.org/areas-de-trabajo/extrayendo-transparencia/) and Yale University (with [J Stallman, PhD Candidate in Economics liaising](https://stallman-j.github.io/)). 

If you're a collaborator on this project working with internal documentation and need access to files *not* housed in this repo, you should first get an account with [PCloud](https://www.pcloud.com/), a virtual drive that's like Dropbox but with nicer storage properties. Once you've done that, email [J Stallman](mailto:j.stallman@yale.edu) who will send you the password and link.

The title of this repository borrows from the "ideal thought experiment": to determine the effect of a particular intervention, one would ideally implement the initiative in randomly selected geographical units. In practice, this is rarely feasible in such a blunt manner.

Nothing stops us from selecting our project name in this manner, however! 

Buena Fé was chosen among Ecuador's cantons at random. You can see a vignette of the R code which implemented this randomization [here](https://stallman-j.github.io/ekonomR/vignettes/basic-mapping/).

```{r, echo = FALSE, fig.cap = "Buena Fé in Ecuador"}
url <- paste0("https://github.com/stallman-j/buena-fe/blob/main/output/03_maps/",paste0("Ecuador_with_1_at-gadm-level_2_randomly-chosen.png?raw=true"))

knitr::include_graphics(url)

```
