```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Buena Fé

This is a GitHub repository holding public collaboration documentation and code for a collaborative project regarding transparency in Ecuador, institutional capacity, and citizen involvement between the [Inter-American Development Bank Andean Group](https://www.iadb.org/en/who-we-are/how-we-are-organized/departments-offices-and-sectors/country-department-andean-group) (liaised by Osmel Manzano and Daniela Valdivia), [FARO](https://grupofaro.org/areas-de-trabajo/extrayendo-transparencia/) and Yale University (with [Jillian Stallman, PhD Candidate in Economics as the liaison](https://stallman-j.github.io/)). 

The title of this repo borrows from an ideal vision of the project: to determine the effect of a particular initiative, one would ideally select geographical units at random. In practice, this is rarely feasible in such a simple way. However, we were able to achieve this in the naming process. Buena Fé was chosen among Ecuador's cantons at random.

```{r, echo = FALSE}
url <- paste0("https://github.com/stallman-j/buena-fe/blob/main/output/03_maps/",paste0("Ecuador_with_1_at-gadm-level_2_randomly-chosen.png?raw=true"))

knitr::include_graphics(url)

```
